### 2018-06-14 express2018/formal.tex
text

We highlight here a formalisation of CCS
in the HOL theorem
prover (HOL4) \cite{slind2008brief},
including the new concepts and theorems proposed in the first half of
this paper.
%  The main purpose is to convince the readers that, there's no flaw
%  in the informal proofs. 
The whole formalisation can be found 
in \cite{Tian:2017wrba}  or in 
 in the official example folder of HOL4 source
code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}. The
work consists of about 20,000 lines of proof scripts in Standard ML,
derived from an early work \cite{Nesi:1992ve} by Monica Nesi in 1992-1995.

HOL4 is written in Standard ML (ML for abbreviation), which plays three roles here:
\begin{enumerate}
\item It serves as the underlying implementation language for the core HOL engine;
\item It's used to implement tactics (and tacticals) for writing proofs;
\item It's used as the command language of the HOL interactive shell.
\end{enumerate}
Besides, HOL4 users can write arbitrary applications which leverages
the theorem proving facility. The HOL logic language, on the other
side, is more close to Classic ML, in which the early HOL systems were built.

>>>>

We highlight here a formalisation of CCS
in the HOL theorem
prover (HOL4) \cite{slind2008brief},
including the new concepts and theorems proposed in the first half of
this paper.
%  The main purpose is to convince the readers that, there's no flaw
%  in the informal proofs. 
The whole formalisation can be found 
in \cite{Tian:2017wrba}  or in 
 in the official example folder of HOL4 source
code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}. The
work consists of about 20,000 lines of proof scripts in Standard ML
(and that follows the pioneering work by Nesi \cite{Nesi:1992ve}, in
1992-1995).

HOL4 is written in Standard ML (ML for abbreviation), which plays three roles here:
\begin{enumerate}
\item It serves as the underlying implementation language for the core HOL engine;
\item It's used to implement tactics (and tacticals) for writing proofs;
\item It's used as the command language of the HOL interactive shell.
\end{enumerate}
HOL4 users can write arbitrary applications which leverage
the theorem proving facility. 
\iflong
The HOL logic language, on the other
 side, is more close to Classic ML, in which the early HOL systems were built.
\DS{removed the sentence because  it did not
  seem important} 
\fi
